### 2023-04-13 chapter2/chapter2.tex
Added clarification about motif counts and removed simulation methods section
Added OGid to scores figure caption

\section{Results}
\begin{figure}[h!]
\includegraphics[width=\textwidth]{scores/out/scores_07E3.png}
\centering
\caption{\textbf{Analyses of disorder scores.}
\textbf{(A)} Example alignment with the disorder scores of its sequences. Higher scores indicate a higher probability of disorder. Disorder score traces are colored by the position of its associated species on the phylogenetic tree. \textbf{(B)} Correlations between disorder scores and feature contrasts in regions. Asterisks indicate statistically significant correlations as computed by permutation tests ($p < 0.001$). \textbf{(C-D)} Example scatter plots showing correlations plotted in panel B. \textbf{(E)} GO term analysis of regions with rapidly evolving disorder scores. Only terms whose $p$-values are below 0.001 are shown.}
\label{fig:scores}
\end{figure}

@@

\subsection{Definition and calculation of features}
Features were calculated as in Zarin \textit{et al.} with the following modifications~\cite{Zarin2019}. The regular expression for polar residue fraction was [QNSTCH], which, in contrast to the original study, excludes glycine residues. Additionally, length, expressed in log scale, was replaced with a feature proportional radius of gyration for an excluded-volume polymer~\cite{Flory1949}. Because the radii of gyration of chemically denatured proteins closely match the values expected for equivalent random coils, we felt this feature would better capture the relationship between an IDR's length and its biophysical properties~\cite{Kohn2004}. Finally, several motifs from ELM were replaced with their metazoan counterparts or updated versions of the same entries~\cite{Kumar2021}. These differences are noted in the supplementary data. Kappa, omega, SCD, hydropathy, PPII propensity, and Wootton-Federhen sequence complexity were calculated with localCIDER 0.1.19~\cite{Holehouse2017}. Isoelectric point was calculated with the Python package isoelectric, which is available on PyPI or at \url{https://isoelectric.org/}~\cite{Kozlowski2016}. Otherwise, features were calculated with custom code. A full list of features and their definitions is given in Table~\ref{stable:features} and Table~\ref{stable:regexes}.

@@

\subsection{Simulation analyses}

>>>>

\section{Results}
\begin{figure}[h!]
\includegraphics[width=\textwidth]{scores/out/scores_07E3.png}
\centering
\caption{\textbf{Analyses of disorder scores.}
\textbf{(A)} Example region in the alignment of the sequences in orthologous group 07E3 with their corresponding disorder scores. Higher scores indicate a higher probability of disorder. Disorder score traces are colored by the position of its associated species on the phylogenetic tree. \textbf{(B)} Correlations between disorder scores and feature contrasts in regions. Asterisks indicate statistically significant correlations as computed by permutation tests ($p < 0.001$). \textbf{(C-D)} Example scatter plots showing correlations plotted in panel B. \textbf{(E)} GO term analysis of regions with rapidly evolving disorder scores. Only terms whose $p$-values are below 0.001 are shown.}
\label{fig:scores}
\end{figure}

@@

\subsection{Definition and calculation of features}
Features were calculated as in Zarin \textit{et al.} with the following modifications~\cite{Zarin2019}. The regular expression for polar residue fraction was [QNSTCH], which, in contrast to the original study, excludes glycine residues. Additionally, length, expressed in log scale, was replaced with a feature proportional radius of gyration for an excluded-volume polymer~\cite{Flory1949}. Because the radii of gyration of chemically denatured proteins closely match the values expected for equivalent random coils, we felt this feature would better capture the relationship between an IDR's length and its biophysical properties~\cite{Kohn2004}. Finally, several motifs from ELM were replaced with their metazoan counterparts or updated versions of the same entries~\cite{Kumar2021}. Furthermore, unlike the previous work, motifs were left as counts and not normalized to the proteome-wide average. These differences are noted in the supplementary data. Kappa, omega, SCD, hydropathy, PPII propensity, and Wootton-Federhen sequence complexity were calculated with localCIDER 0.1.19~\cite{Holehouse2017}. Isoelectric point was calculated with the Python package isoelectric, which is available on PyPI or at \url{https://isoelectric.org/}~\cite{Kozlowski2016}. Otherwise, features were implemented with custom code. A full list of features and their definitions is given in Table~\ref{stable:features} and Table~\ref{stable:regexes}.

@@
